---
title: "high school quality app"
author: "Enrique Olivo eco2121"
date: "October 7, 2017"
output: html_document
---
## LOADING IN THE DATA

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Function to read Excel files with multiple sheets
#Must install appropriate Perl Interpreter, or find alternative way to read the Report
#https://www.activestate.com/activeperl/downloads

library(gdata)
perl <- "C:/Perl64/bin/perl5.24.2.exe"


#Student Achievement (SA)
data.sa <- read.xls("C:/Users/enriquethemoist/Dropbox/Columbia Work/4A - one/Applied Data Science/Project 2/HS.xlsx", 
                  sheet=2, perl=perl)

#Closing the Achievement Gap (CAG)
data.cag <- read.xls("C:/Users/enriquethemoist/Dropbox/Columbia Work/4A - one/Applied Data Science/Project 2/HS.xlsx", 
                  sheet=3, perl=perl)


#Framework Sheet (framework)
data.framework <- read.xls("C:/Users/enriquethemoist/Dropbox/Columbia Work/4A - one/Applied Data Science/Project 2/HS.xlsx", 
                  sheet=4, perl=perl)

#Additional Info (AI)
data.ai <- read.xls("C:/Users/enriquethemoist/Dropbox/Columbia Work/4A - one/Applied Data Science/Project 2/HS.xlsx", 
                  sheet=5, perl=perl)


```

## QUALITATIVE SURVEY RANKINGS separating them into separate dataframes based on the topic of their survey


```{r cars}
#Overall ranking of Schools, taking the average across Individual Categories and then across ALL Categories

##Rigorous Instruction
#X5, percent positive responses on school survey
#x8, percentage of students who say they learn a lot from feedback
#x10, % of students who know what their teacher wants them to learn from class
#x12, % of teachers who say that students build on each others' ideas during class

#extracting the specific columns 
data.framework.RI <- subset(data.framework, select=c("Framework", "X", "X.5", "X.8", "X.10", "X.12"))



##Collaborative Teachers
#x16, percent positive responses on school survey
#x19, % of teachers who say that they work together to design instructional programs
#x21, % of teachers who say that they have opportunities to work productively with colleagues
#x23, % of teachers who say that they feel responsible that all students learn

#extracting the specific columns
data.framework.CT <- subset(data.framework, select=c("Framework", "X", "X.16", "X.19", "X.21", "X.23"))




##Supportive Environment
#x27, percent positive responses on school survey
#x30, % of students who feel safe in the hallways, bathrooms, locker room, & cafeteria
#x32, % of students who say that teachers notice when they are upset or have emotional difficulty
#x34, % of students who say that school supports navigating post-secondary process
#x44, percentage of students with 90+% attendance

#extracting the specific columns
data.framework.SE <- subset(data.framework, select=c("Framework", "X", "X.27", "X.30", "X.32", "X.34", "X.44"))



##Effective School Leadership
#x47, percentage of positive responses
#x49, % of teachers who say that the principal communicates a clear vision for the school
#x51, % of teachers...that curriculum and instruction are well coordinated across different grade levels
#x53, % of parents who feel that the principals works to create a sense of community in the school

#extracting the specific columns
data.framework.ESL <- subset(data.framework, select=c("Framework", "X", "X.47", "X.49", "X.51", "X.53"))



##Strong Family-Community Ties
#x56, percentage of positive responses
#x59, % of parents who say that school staff regularly communicate with them about how the staff can help their children learn
#x61, % of parents who feel that teachers try to understand families' problems and concerns
#x63, % of teachers who say that teachers at this school work closely with families to meet students' needs

#extracting the specific columns
data.framework.SFCT <- subset(data.framework, select=c("Framework", "X", "X.56", "X.59", "X.61", "X.63"))



##Trust
#x66, percentage of positive responses
#x69, % of teachers who say that they trust the principal
#x71, % of teachers who say that they trust each other
#x73, % of parents who say that school staff work hard to build lasting relationships with them
#x75, % of students who say that teachers treat them with respect

#extracting the specific columns
data.framework.T <- subset(data.framework, select=c("Framework", "X", "X.66", "X.69", "X.71", "X.73", "X.75"))


```

## Analysis on each individual survey category

##RIGOROUS INSTRUCTION




```{r}

##RIGOROUS INSTRUCTION
#removing the first row 
data.framework.RI <- data.framework.RI[-1,]

#separate the columns with and without percentages
RI.percentages <- data.framework.RI[,-c(1,2)]

RI.nopercentages <- data.framework.RI[,-c(3,4,5,6)]


#removing percentage signs
(RI.numbers <- data.frame(sapply(RI.percentages, function(x) as.numeric(gsub("%", "", x)))))

#add them back to the original dataframe
RI.nopercentages$X.5 <- RI.numbers$X.5
RI.nopercentages$X.8 <- RI.numbers$X.8
RI.nopercentages$X.10 <- RI.numbers$X.10
RI.nopercentages$X.12 <- RI.numbers$X.12

#Take the average of the surveys, and add them to their own column
RI.nopercentages$average <- ave(RI.nopercentages$X.5, RI.nopercentages$X.8, RI.nopercentages$X.10, RI.nopercentages$X.12)

#Order them from lowest to highest, across 487 observations
RI.nopercentages <- RI.nopercentages[order(RI.nopercentages$average),]


```

##COLLABORATIVE TEACHERS

```{r}

##COLLABORATIVE TEACHERS
#removing the first row 
data.framework.CT <- data.framework.CT[-1,]

#separate the columns with and without percentages
CT.percentages <- data.framework.CT[,-c(1,2)]

CT.nopercentages <- data.framework.CT[,-c(3,4,5,6)]

#removing percentage signs
(CT.numbers <- data.frame(sapply(CT.percentages, function(x) as.numeric(gsub("%", "", x)))))


#add them back to the original dataframe
CT.nopercentages$X.16 <- CT.numbers$X.16
CT.nopercentages$X.19 <- CT.numbers$X.19
CT.nopercentages$X.21 <- CT.numbers$X.21
CT.nopercentages$X.23 <- CT.numbers$X.23

#Take the average of the surveys, and add them to their own column
CT.nopercentages$average <- ave(CT.nopercentages$X.16, CT.nopercentages$X.19, CT.nopercentages$X.21, CT.nopercentages$X.23)

#Order them from lowest to highest, across 487 observations
CT.nopercentages <- CT.nopercentages[order(CT.nopercentages$average),]


```

##SUPPORTIVE ENVIRONMENT

```{r}

##Supportive Environment
#x27, percent positive responses on school survey
#x30, % of students who feel safe in the hallways, bathrooms, locker room, & cafeteria
#x32, % of students who say that teachers notice when they are upset or have emotional difficulty
#x34, % of students who say that school supports navigating post-secondary process
#x44, percentage of students with 90+% attendance

#extracting the specific columns
data.framework.SE <- subset(data.framework, select=c("Framework", "X", "X.27", "X.30", "X.32", "X.34", "X.44"))

#removing the first row 
data.framework.SE <- data.framework.SE[-1,]

#separate the columns with and without percentages
SE.percentages <- data.framework.SE[,-c(1,2)]

SE.nopercentages <- data.framework.SE[,-c(3,4,5,6,7)]


#removing percentage signs
(SE.numbers <- data.frame(sapply(SE.percentages, function(x) as.numeric(gsub("%", "", x)))))



#round the last column
SE.numbers$X.44 <- round(SE.numbers$X.44)

#add them back to the original dataframe
SE.nopercentages$X.27 <- SE.numbers$X.27
SE.nopercentages$X.30 <- SE.numbers$X.30
SE.nopercentages$X.32 <- SE.numbers$X.32
SE.nopercentages$X.34 <- SE.numbers$X.34
SE.nopercentages$X.44 <- SE.numbers$X.44

#Take the average of the surveys, and add them to their own column
SE.nopercentages$average <- ave(SE.nopercentages$X.27, SE.nopercentages$X.30, SE.nopercentages$X.32, SE.nopercentages$X.34, SE.nopercentages$X.44)

#Order them from lowest to highest, across 487 observations
SE.nopercentages <- SE.nopercentages[order(SE.nopercentages$average),]


```

##EFFECTIVE SCHOOL LEADERSHIP

```{r}
##Effective School Leadership
#x47, percentage of positive responses
#x49, % of teachers who say that the principal communicates a clear vision for the school
#x51, % of teachers...that curriculum and instruction are well coordinated across different grade levels
#x53, % of parents who feel that the principals works to create a sense of community in the school

#extracting the specific columns
data.framework.ESL <- subset(data.framework, select=c("Framework", "X", "X.47", "X.49", "X.51", "X.53"))


#removing the first row 
data.framework.ESL <- data.framework.ESL[-1,]

#separate the columns with and without percentages
ESL.percentages <- data.framework.ESL[,-c(1,2)]

ESL.nopercentages <- data.framework.ESL[,-c(3,4,5,6)]


#removing percentage signs
(ESL.numbers <- data.frame(sapply(ESL.percentages, function(x) as.numeric(gsub("%", "", x)))))


#add them back to the original dataframe
ESL.nopercentages$X.47 <- ESL.numbers$X.47
ESL.nopercentages$X.49 <- ESL.numbers$X.49
ESL.nopercentages$X.51 <- ESL.numbers$X.51
ESL.nopercentages$X.53 <- ESL.numbers$X.53

#Take the average of the surveys, and add them to their own column
ESL.nopercentages$average <- ave(ESL.nopercentages$X.47, ESL.nopercentages$X.49, ESL.nopercentages$X.51, ESL.nopercentages$X.53)

#Order them from lowest to highest, across 487 observations
ESL.nopercentages <- ESL.nopercentages[order(ESL.nopercentages$average),]


```

##STRONG FAMILY COMMUNITY TIES

```{r}

##Strong Family-Community Ties
#x56, percentage of positive responses
#x59, % of parents who say that school staff regularly communicate with them about how the staff can help their children learn
#x61, % of parents who feel that teachers try to understand families' problems and concerns
#x63, % of teachers who say that teachers at this school work closely with families to meet students' needs

#removing the first row 
data.framework.SFCT <- data.framework.SFCT[-1,]

#separate the columns with and without percentages
SFCT.percentages <- data.framework.SFCT[,-c(1,2)]

SFCT.nopercentages <- data.framework.SFCT[,-c(3,4,5,6)]


#removing percentage signs
(SFCT.numbers <- data.frame(sapply(SFCT.percentages, function(x) as.numeric(gsub("%", "", x)))))


#add them back to the original dataframe
SFCT.nopercentages$X.56 <- SFCT.numbers$X.56
SFCT.nopercentages$X.59 <- SFCT.numbers$X.59
SFCT.nopercentages$X.61 <- SFCT.numbers$X.61
SFCT.nopercentages$X.63 <- SFCT.numbers$X.63

#Take the average of the surveys, and add them to their own column
SFCT.nopercentages$average <- ave(SFCT.nopercentages$X.56, SFCT.nopercentages$X.59, SFCT.nopercentages$X.61, SFCT.nopercentages$X.63)

#Order them from lowest to highest, across 487 observations
SFCT.nopercentages <- SFCT.nopercentages[order(SFCT.nopercentages$average),]


```

##TRUST

```{r}
##Trust
#x66, percentage of positive responses
#x69, % of teachers who say that they trust the principal
#x71, % of teachers who say that they trust each other
#x73, % of parents who say that school staff work hard to build lasting relationships with them
#x75, % of students who say that teachers treat them with respect

#removing the first row 
data.framework.T <- data.framework.T[-1,]

#separate the columns with and without percentages
T.percentages <- data.framework.T[,-c(1,2)]

T.nopercentages <- data.framework.T[,-c(3,4,5,6,7)]


#removing percentage signs
(T.numbers <- data.frame(sapply(T.percentages, function(x) as.numeric(gsub("%", "", x)))))


#add them back to the original dataframe
T.nopercentages$X.66 <- T.numbers$X.66
T.nopercentages$X.69 <- T.numbers$X.69
T.nopercentages$X.71 <- T.numbers$X.71
T.nopercentages$X.73 <- T.numbers$X.73
T.nopercentages$X.75 <- T.numbers$X.75


#Take the average of the surveys, and add them to their own column
T.nopercentages$average <- ave(T.nopercentages$X.66, T.nopercentages$X.69, T.nopercentages$X.71, T.nopercentages$X.73, T.nopercentages$X.75)

#Order them from lowest to highest, across 487 observations
T.nopercentages <- T.nopercentages[order(T.nopercentages$average),]

```

##RANKING ACROSS ALL SURVEY TOPICS: Rigorous Instruction, Collaborative Teachers, Supportive Environment, Effective School Leadership, Strong Family-Community Ties

```{r}
data.framework.allsurvey <- subset(data.framework, select=c("Framework", "X", "X.5", "X.8", "X.10", "X.12", "X.16", "X.19", "X.21", "X.23", "X.27", "X.30", "X.32", "X.34", "X.44", "X.47", "X.49", "X.51", "X.53", "X.56", "X.59", "X.61", "X.63", "X.66", "X.69", "X.71", "X.73", "X.75" ))

#removing the first row 
data.framework.allsurvey <- data.framework.allsurvey[-1,]

#separate the columns with and without percentages
allsurvey.percentages <- data.framework.allsurvey[,-c(1,2)]

allsurvey.nopercentages <-data.framework.allsurvey[,-c(3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28)]


#removing percentage signs
(allsurvey.numbers <- data.frame(sapply(allsurvey.percentages, function(x) as.numeric(gsub("%", "", x)))))



#round that one column
allsurvey.numbers$X.44 <- round(allsurvey.numbers$X.44)

#add them back to the original dataframe
allsurvey.nopercentages$X.5 <- allsurvey.numbers$X.5
allsurvey.nopercentages$X.8 <- allsurvey.numbers$X.8
allsurvey.nopercentages$X.10 <- allsurvey.numbers$X.10
allsurvey.nopercentages$X.12 <- allsurvey.numbers$X.12
allsurvey.nopercentages$X.16 <- allsurvey.numbers$X.16
allsurvey.nopercentages$X.19 <- allsurvey.numbers$X.19
allsurvey.nopercentages$X.21 <- allsurvey.numbers$X.21
allsurvey.nopercentages$X.23 <- allsurvey.numbers$X.23
allsurvey.nopercentages$X.27 <- allsurvey.numbers$X.27
allsurvey.nopercentages$X.30 <- allsurvey.numbers$X.30
allsurvey.nopercentages$X.32 <- allsurvey.numbers$X.32
allsurvey.nopercentages$X.34 <- allsurvey.numbers$X.34
allsurvey.nopercentages$X.44 <- allsurvey.numbers$X.44
allsurvey.nopercentages$X.47 <- allsurvey.numbers$X.47
allsurvey.nopercentages$X.49 <- allsurvey.numbers$X.49
allsurvey.nopercentages$X.51 <- allsurvey.numbers$X.51
allsurvey.nopercentages$X.53 <- allsurvey.numbers$X.53
allsurvey.nopercentages$X.56 <- allsurvey.numbers$X.56
allsurvey.nopercentages$X.59 <- allsurvey.numbers$X.59
allsurvey.nopercentages$X.61 <- allsurvey.numbers$X.61
allsurvey.nopercentages$X.63 <- allsurvey.numbers$X.63
allsurvey.nopercentages$X.66 <- allsurvey.numbers$X.66
allsurvey.nopercentages$X.69 <- allsurvey.numbers$X.69
allsurvey.nopercentages$X.71 <- allsurvey.numbers$X.71
allsurvey.nopercentages$X.73 <- allsurvey.numbers$X.73
allsurvey.nopercentages$X.75 <- allsurvey.numbers$X.75

#Take the average of the surveys, and add them to their own column

blank<-NULL
for (i in 1:nrow(allsurvey.nopercentages)){
  blank[i] <- round(sum(allsurvey.nopercentages[i,3:28])/26)
}

allsurvey.nopercentages$average <- blank

#Order them from lowest to highest, across 487 observations
allsurvey.nopercentages <- allsurvey.nopercentages[order(allsurvey.nopercentages$average),]


```

##QUANTITATIVE METRICS I
- Graduation Rate (SA)
- Postsecondary Enrollment Rate, 6 months (SA)

    
```{r}
##Extracting Graduation Rate, and Post-secondary Enrollment Rate
#x.76 graduation rate
#x.118 postsecondary enrollment

data.sa.quant <- subset(data.sa, select=c("Student.Achievement", "X", "X.76", "X.118"))

#removing the first row 
data.sa.quant <- data.sa.quant[-1,]

#separate the columns with and without percentages
data.sa.quant.percentages <- data.sa.quant[,-c(1,2)]

data.sa.quant.nopercentages <-data.sa.quant[,-c(3,4)]


#removing percentage signs
(data.sa.quant.numbers <- data.frame(sapply(data.sa.quant.percentages, function(x) as.numeric(gsub("%", "", x)))))


#round the columns
data.sa.quant.numbers$X.76 <- round(data.sa.quant.numbers$X.76)
data.sa.quant.numbers$X.118 <- round(data.sa.quant.numbers$X.118)

#add them back to the original dataframe
data.sa.quant.nopercentages$X.76 <- data.sa.quant.numbers$X.76
data.sa.quant.nopercentages$X.118 <- data.sa.quant.numbers$X.118

#Take the average of the surveys, and add them to their own column

blank<-NULL
for (i in 1:nrow(data.sa.quant.nopercentages)){
  blank[i] <- round(sum(data.sa.quant.nopercentages[i,3:4])/2)
}

data.sa.quant.nopercentages$average <- blank


#Order them from lowest to highest, across 487 observations
data.sa.quant.nopercentages <- data.sa.quant.nopercentages[order(data.sa.quant.nopercentages$average),]

##SOME MISSING VARIABLES THEREFORE NO AVAILABLE AVERAGE
```

##QUANTITATIVE METRICS II

- Average Score by subject (Additional Info)
    - Algebra
    - Geometry
    - English
    - US History
    - Global History
    - Chemistry
    - Physics
    
```{r}
#X.1 average algebra 
#X.4 average geometry
#X.10 average english
#X.13 average US History
#X.15 average Global History
#X.18 average chemistry
#X.20 average physics

#Altogether
data.allsubjects <- subset(data.ai, select=c("Additional.Info", "X","X.1","X.4","X.10","X.13","X.15","X.18","X.20"))

#Across 4 subjects!
data.math <- subset(data.ai, select=c("Additional.Info","X", "X.1","X.4"))
data.english <-subset(data.ai, select=c("Additional.Info","X","X.10"))
data.history <- subset(data.ai, select=c("Additional.Info","X","X.13","X.15"))
data.science <- subset(data.ai, select=c("Additional.Info", "X","X.18","X.20"))

#removing the first row
data.allsubjects <- data.allsubjects[-1,]
data.math <- data.math[-1,]
data.english <- data.english[-1,]
data.history <- data.history[-1,]
data.science <- data.science

#separate the columns with and without percentages
data.allsubjects.percentages <- data.allsubjects[,-c(1,2)]
data.math.percentages <- data.math[,-c(1,2)]
#data.english.percentages <- (data.english[,-c(1,2)]) #unnecessary
data.history.percentages <- data.history[,-c(1,2)]
data.science.percentages <- data.science[,-c(1,2)]

data.allsubjects.nopercentages <-data.allsubjects[,-c(3,4,5,6,7,8,9)] 
data.math.nopercentages <- data.math[,-c(3,4)]
data.english.nopercentages <- data.english[,-3]
data.history.nopercentages <- data.history[,-c(3,4)]
data.science.nopercentages <- data.science[,-c(3,4)]


#removing percentage signs
(data.allsubjects.numbers <- data.frame(sapply(data.allsubjects.percentages, function(x) as.numeric(gsub("%", "", x)))))

(data.math.numbers <- data.frame(sapply(data.math.percentages, function(x) as.numeric(gsub("%", "", x)))))

#(data.english.numbers <- data.frame(sapply(data.english.percentages, function(x) as.numeric(gsub("%", "", x)))))

(data.history.numbers <- data.frame(sapply(data.history.percentages, function(x) as.numeric(gsub("%", "", x)))))

(data.science.numbers <- data.frame(sapply(data.science.percentages, function(x) as.numeric(gsub("%", "", x)))))

#round the columns
data.allsubjects.numbers$X.18 <- round(data.allsubjects.numbers$X.18)
data.science.numbers$X.18 <- round(data.science.numbers$X.18)

#add them back to the original dataframe
data.allsubjects.nopercentages$X.1 <- data.allsubjects.numbers$X.1
data.allsubjects.nopercentages$X.4 <- data.allsubjects.numbers$X.4
data.allsubjects.nopercentages$X.10 <- data.allsubjects.numbers$X.10
data.allsubjects.nopercentages$X.13 <- data.allsubjects.numbers$X.13
data.allsubjects.nopercentages$X.15 <- data.allsubjects.numbers$X.15
data.allsubjects.nopercentages$X.18 <- data.allsubjects.numbers$X.18
data.allsubjects.nopercentages$X.20 <- data.allsubjects.numbers$X.20

data.math.nopercentages$X.1 <- data.math.numbers$X.1
data.math.nopercentages$X.4 <- data.math.numbers$X.4

#data.english.nopercentages$X.10 <- data.english.percentages #unnecessary

data.history.nopercentages$X.13 <- data.history.numbers$X.13
data.history.nopercentages$X.15 <- data.allsubjects.numbers$X.15

data.science.nopercentages$X.18 <- data.science.numbers$X.18
data.science.nopercentages$X.20 <- data.science.numbers$X.20

#Take the average of the surveys, and add them to their own column

blank.1<-NULL
for (i in 1:nrow(data.allsubjects.nopercentages)){
  blank.1[i] <- round(sum(data.allsubjects.nopercentages[i,3:9])/7)
}
data.allsubjects.nopercentages$average <- blank.1

blank.2<-NULL
for (i in 1:nrow(data.math.nopercentages)){
  blank.2[i] <- round(sum(data.math.nopercentages[i,3:4])/2)
}
data.math.nopercentages$average <- blank.2

#blank.3<-NULL
#for (i in 1:nrow(data.english.nopercentages)){
#  blank.3[i] <- round(sum(data.english.nopercentages[i,3])/2)
#}
#data.english.nopercentages$average <- blank.3
#only one value... no "average" to take!!!

blank.4<-NULL
for (i in 1:nrow(data.history.nopercentages)){
  blank.4[i] <- round(sum(data.history.nopercentages[i,3:4])/2)
}
data.history.nopercentages$average <- blank.4

blank.5<-NULL
for (i in 1:nrow(data.science.nopercentages)){
  blank.5[i] <- round(sum(data.science.nopercentages[i,3:4])/2)
}
data.science.nopercentages$average <- blank.5

#Order them from lowest to highest, across 487 observations

data.allsubjects <- data.allsubjects.nopercentages[order(data.allsubjects.nopercentages$average),]

data.math <- data.math.nopercentages[order(data.math.nopercentages$average),]
data.english <- data.english[order(data.english$X.10),]
#english has some missing values that appear as blank
data.history <- data.history.nopercentages[order(data.history.nopercentages$average),]
data.science <- data.science.nopercentages[order(data.science.nopercentages$average),]

##SOME MISSING VARIABLES THEREFORE NO AVAILABLE AVERAGE

head(data.english)

```



##RENAME FINAL DATAFRAMES 

```{r}
#Qualitative Survey Data
data.ranked.RI <- RI.nopercentages
data.ranked.CT <- CT.nopercentages
data.ranked.SE <- SE.nopercentages
data.ranked.ESL <- ESL.nopercentages
data.ranked.SFCT <- SFCT.nopercentages
data.ranked.T <- T.nopercentages
data.ranked.allsurvey <- allsurvey.nopercentages

#Quanitative Metrics
data.ranked.quant <- data.sa.quant.nopercentages #grad and postsec enrollment rates

#Subjects
data.ranked.allsubjects <- data.allsubjects
data.ranked.math <- data.math
data.ranked.english <- data.english
data.ranked.history <- data.history
data.ranked.science <- data.science

```

##FURTHER CLEANING OF FINAL DATAFRAMES
- Descending Order
- Cut, Rename, And Percentize irrelevant columns

```{r}
##################
#Descending Order#
##################
data.ranked.RI <- data.ranked.RI[order(-data.ranked.RI$average),]
data.ranked.CT <- data.ranked.CT[order(-data.ranked.CT$average),]
data.ranked.SE <- data.ranked.SE[order(-data.ranked.SE$average),]
data.ranked.ESL <- data.ranked.ESL[order(-data.ranked.ESL$average),]
data.ranked.SFCT <- data.ranked.SFCT[order(-data.ranked.SFCT$average),]
data.ranked.T <- data.ranked.T[order(-data.ranked.T$average),]
data.ranked.allsurvey <- data.ranked.allsurvey[order(-data.ranked.allsurvey$average),]

data.ranked.quant <- data.ranked.quant[order(-data.ranked.quant$average),]

data.ranked.allsubjects <- data.ranked.allsubjects[order(-data.ranked.allsubjects$average),]
data.ranked.math <- data.ranked.math[order(-data.ranked.math$average),]
#X.10 in English is actually a factor, change to numeric and then sort
data.ranked.english[, 3] <- as.numeric(as.character( data.ranked.english[, 3] )) 
data.ranked.english <- data.ranked.english[order(-data.ranked.english$X.10),]
data.ranked.history <- data.ranked.history[order(-data.ranked.history$average),]
data.ranked.science <- data.ranked.science[order(-data.ranked.science$average),]

######################
#Cut, Rename, Percentize Columns#
######################

#RI 
head(data.ranked.RI)
data.ranked.RI$X.5 <- NULL
data.ranked.RI$X.8 <- NULL
data.ranked.RI$X.10 <- NULL
data.ranked.RI$X.12 <- NULL
colnames(data.ranked.RI) <- c("Ranking","School Name", "Averaged Score (%)")
ranks <- c(1:487)
data.ranked.RI$Ranking <- ranks
rownames(data.ranked.RI) <- NULL

#CT
head(data.ranked.CT)
dim(data.ranked.CT)
data.ranked.CT$average <- round(data.ranked.CT$average)
data.ranked.CT$X.16 <- NULL
data.ranked.CT$X.19 <- NULL
data.ranked.CT$X.21 <- NULL
data.ranked.CT$X.23 <- NULL
colnames(data.ranked.CT) <- c("Ranking", "School Name", "Averaged Score (%)")
data.ranked.CT$Ranking <- ranks
rownames(data.ranked.CT) <- NULL

#SE
head(data.ranked.SE)
dim(data.ranked.SE)
data.ranked.SE$X.27 <- NULL
data.ranked.SE$X.30 <- NULL
data.ranked.SE$X.32 <- NULL
data.ranked.SE$X.34 <- NULL
data.ranked.SE$X.44 <- NULL
colnames(data.ranked.SE) <- c("Ranking", "School Name", "Averaged Score (%)")
data.ranked.SE$Ranking <- ranks
head(data.ranked.SE)
rownames(data.ranked.SE) <- NULL

#ESL
head(data.ranked.ESL)
dim(data.ranked.ESL)
data.ranked.ESL$X.47 <- NULL
data.ranked.ESL$X.49 <- NULL
data.ranked.ESL$X.51 <- NULL
data.ranked.ESL$X.53 <- NULL
colnames(data.ranked.ESL) <- c("Ranking", "School Name", "Averaged Score (%)")
data.ranked.ESL$Ranking <- ranks
head(data.ranked.ESL)
rownames(data.ranked.ESL) <- NULL

#SFCT
head(data.ranked.SFCT)
dim(data.ranked.SFCT)
data.ranked.SFCT$X.56 <- NULL
data.ranked.SFCT$X.59 <- NULL
data.ranked.SFCT$X.61 <- NULL
data.ranked.SFCT$X.63 <- NULL
colnames(data.ranked.SFCT) <- c("Ranking", "School Name", "Averaged Score (%)")
data.ranked.SFCT$Ranking <- ranks
head(data.ranked.SFCT)
rownames(data.ranked.SFCT) <- NULL

#T
head(data.ranked.T)
dim(data.ranked.T)
data.ranked.T$X.66 <- NULL
data.ranked.T$X.69 <- NULL
data.ranked.T$X.71 <- NULL
data.ranked.T$X.73 <- NULL
data.ranked.T$X.75 <- NULL
colnames(data.ranked.T) <- c("Ranking", "School Name", "Averaged Score (%)")
data.ranked.T$Ranking <- ranks
head(data.ranked.T)
rownames(data.ranked.T) <- NULL

#allsurvey
head(data.ranked.allsurvey)
dim(data.ranked.allsurvey)
data.ranked.allsurvey$X.5 <- NULL
data.ranked.allsurvey$X.8 <- NULL
data.ranked.allsurvey$X.10 <- NULL
data.ranked.allsurvey$X.12 <- NULL
data.ranked.allsurvey$X.16 <- NULL
data.ranked.allsurvey$X.19 <- NULL
data.ranked.allsurvey$X.21 <- NULL
data.ranked.allsurvey$X.23 <- NULL
data.ranked.allsurvey$X.27 <- NULL
data.ranked.allsurvey$X.30 <- NULL
data.ranked.allsurvey$X.32 <- NULL
data.ranked.allsurvey$X.34 <- NULL
data.ranked.allsurvey$X.44 <- NULL
data.ranked.allsurvey$X.47 <- NULL
data.ranked.allsurvey$X.49 <- NULL
data.ranked.allsurvey$X.51 <- NULL
data.ranked.allsurvey$X.53 <- NULL
data.ranked.allsurvey$X.56 <- NULL
data.ranked.allsurvey$X.59 <- NULL
data.ranked.allsurvey$X.61 <- NULL
data.ranked.allsurvey$X.63 <- NULL
data.ranked.allsurvey$X.66 <- NULL
data.ranked.allsurvey$X.69 <- NULL
data.ranked.allsurvey$X.71 <- NULL
data.ranked.allsurvey$X.73 <- NULL
data.ranked.allsurvey$X.75 <- NULL
colnames(data.ranked.allsurvey) <- c("Ranking", "School Name", "Averaged Score (%)")
data.ranked.allsurvey$Ranking <- ranks
head(data.ranked.allsurvey)
rownames(data.ranked.allsurvey) <- NULL

#Quant
head(data.ranked.quant)
dim(data.ranked.quant)
colnames(data.ranked.quant) <- c("Ranking", "School Name", "Graduation Rate (%)", "Post-secondary Enrolment Rate, 6 Months (%)", "Averaged Score (%)")
data.ranked.quant$Ranking <- ranks
head(data.ranked.quant)
rownames(data.ranked.quant) <- NULL

#Math
head(data.ranked.math)
colnames(data.ranked.math) <- c("Ranking", "School Name", "Algebra Score (%)", "Geometry Score (%)", "Averaged Math Score (%)")
data.ranked.math$Ranking <- ranks
head(data.ranked.math)
rownames(data.ranked.math) <- NULL

#English
head(data.ranked.english)
colnames(data.ranked.english) <- c("Ranking", "School Name", "English Score (%)")
data.ranked.english$Ranking <- ranks
head(data.ranked.english)
rownames(data.ranked.english) <- NULL

#History
head(data.ranked.history)
colnames(data.ranked.history) <- c("Ranking", "School Name", "US History Score (%)", "Global History Score (%)", "Averaged Score (%)")
data.ranked.history$Ranking <- ranks
head(data.ranked.history)
rownames(data.ranked.history) <- NULL

#Science
head(data.ranked.science)
colnames(data.ranked.science) <- c("Ranking", "School Name", "Chemistry Score (%)", "Physics Score (%)", "Averaged Score (%)")
ranks.2 <- c(1:488)
data.ranked.science$Ranking <- ranks.2
data.ranked.science$Physics <- round(data.ranked.science$Physics)
head(data.ranked.science)
rownames(data.ranked.science) <- NULL

#All Subjects
head(data.ranked.allsubjects)
data.ranked.allsubjects <- data.ranked.allsubjects[,-c(3,4,5,6,7,8,9)]
colnames(data.ranked.allsubjects) <- c("Ranking", "School Name", "Averaged Score - all subjects (%)")
data.ranked.allsubjects$Ranking <- ranks
head(data.ranked.allsubjects)
rownames(data.ranked.allsubjects) <- NULL

```


